---
output: rmarkdown::github_document
---

# simplemagic

Lightweight File 'MIME' Type Detection Based On Contents or Extension

## Description

'MIME' types are shorthand descriptors for file contents and can be
determined from "magic" bytes in file headers, file contents or intuited from
file extensions. Tools are provided to perform limited "magic" tests as well
as mapping 'MIME' types from a database of over 1,500 extension mappings.

Provides a more portable/ligtweight alternative to the `wand` package.

## SOME IMPORTANT DETAILS

The header checking is minimal (i.e. nowhere near as comprehensive as `libmagic`) but covers quite a bit of ground. If there are content-check types from [`magic sources`](https://github.com/threatstack/libmagic/tree/master/magic/) that you would like coded into the package, please file an issue and _include the full line(s)_ from that linked `magic.tab` that you would like mapped.

## What's Inside The Tin

- `get_content_type`:	Discover MIME type of a file based on contents
- `guess_content_type`:	Guess MIME type from filename (extension)
- `simplemagic_mime_db`:	File extension-to-MIME mapping data frame

The following functions are implemented:

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/simplemagic")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(simplemagic)
library(tidyverse)

# current verison
packageVersion("simplemagic")
```

```{r}
list.files(system.file("extdat", package="simplemagic"), full.names=TRUE) %>% 
  map_df(~{
    data_frame(
      fil = basename(.x),
      mime = list(get_content_type(.x))
    )
  }) %>% 
  unnest() %>% 
  print(n=82)
```
